---
title: "Lab 06 - Functions and iterations"
author: "Gabriel Gow s2634184"
date: "`r Sys.Date()`"
output: html_document
---


### Packages and Data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(ggplot2)
```

```{r diamon_rename}
diamonds <- diamonds %>% rename(
    depth_pct = depth,
    length_mm = x,
    width_mm = y,
    depth_mm = z,
    table_pct = table
  )
```


## Exercise 1

```{r}
summary(diamonds)

ggplot(data = diamonds, 
       mapping = aes(x = carat)) + 
  geom_histogram(binwidth = 0.1)

ggplot(data = diamonds, 
       mapping = aes(x = cut)) + 
  geom_bar()

ggplot(data = diamonds, 
       mapping = aes(x = color)) + 
  geom_bar()

ggplot(data = diamonds, 
       mapping = aes(x = clarity)) + 
  geom_bar()

ggplot(data = diamonds, 
       mapping = aes(x = depth_mm)) + 
  geom_histogram(binwidth = 1)

ggplot(data = diamonds, 
       mapping = aes(x = table_pct)) + 
  geom_histogram(binwidth = 1)

ggplot(data = diamonds, 
       mapping = aes(x = price)) + 
  geom_histogram(binwidth = 10)

ggplot(data = diamonds, 
       mapping = aes(x = length_mm)) + 
  geom_histogram(binwidth = 0.25)

ggplot(data = diamonds, 
       mapping = aes(x = width_mm)) + 
  geom_histogram(binwidth = 0.5)

ggplot(data = diamonds, 
       mapping = aes(x = depth_mm)) + 
  geom_histogram(binwidth = 0.5)

ggplot(data = diamonds, 
       mapping = aes(x = carat, y = price)) + 
  geom_point(alpha = 0.5) + 
  geom_smooth(method = lm, 
              se = FALSE) +
  labs(
    x = "carat",
    y = "price",
    title = "carat v price"
  ) +
  theme_bw ()

ggplot(data = diamonds, 
       mapping = aes(
         y = length_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "Length_mm",
    title = "Length in mm - before clean") 

ggplot(data = diamonds, 
       mapping = aes(
         y = depth_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "depth_mm",
    title = "depth in mm - before clean") 

ggplot(data = diamonds, 
       mapping = aes(
         y = width_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "Width_mm",
    title = "Width in mm - before clean") 


diamonds <- diamonds %>%
  filter(length_mm > 0,
    width_mm > 0,
    depth_mm > 0)


ggplot(data = diamonds, 
       mapping = aes(
         y = length_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "Length_mm",
    title = "Length in mm - after clean") 

ggplot(data = diamonds, 
       mapping = aes(
         y = width_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "width_mm",
    title = "width in mm - after clean") 

ggplot(data = diamonds, 
       mapping = aes(
         y = depth_mm)) +
  geom_boxplot(coef = 1,
               lwd = 1.5,
               outlier.shape = 5) +
  labs(
    y = "depth_mm",
    title = "depth in mm - after clean") 
```


## Exercise 2

```{r}

diamonds <- diamonds %>%
  mutate(table_mm = table_pct * width_mm / 100)

# Overall table_mm arithmetic mean?

diamonds %>% summarise(mean_table_mm = mean(table_mm))

# table_mm arithmetic mean within each clarity category

diamonds %>% 
  group_by(clarity) %>%
  summarise(mean_table_mm = mean(table_mm))

```

It seems that the larger diamonds are on average of lower clarity, possibly implying longer/larger diamonds tend to be of worse quality.

```{r}

diamonds %>%
  summarise(across(
    c(carat, depth_pct, table_pct, price, length_mm, width_mm, depth_mm, table_mm), 
    mean, 
    names = "avg.{.col}")
  )

```

## Exercise 3

```{r}
# Write gmean() command

gmean <- function(x){
  return(
    exp(
    sum(
      log(x)
    )
  /
  ( sum(table(x)) )
  ) )
}



```

## Exercise 4

```{r, error = TRUE}

test_data <- list(
  test1 = c(2.1, 3.8, 4.2),
  test2 = c(1, 10, 100, 1000),
  test3 = c(0, 1, 4),
  test4 = c(0.38,  0.94, -1.56),
  test5 = c(TRUE, TRUE),
  test6 = c("6", "7", "8")
)


# Create for loop to test gmean() on the above examples


```


## Exercise 5

```{r}
# Copy gmean() from Ex 3 and edit it to check the input





# Copy your code from Ex 4 to test your new command





```

## Exercise 6

```{r}
# replicate the for loop from Ex 4 using the map (or a similar) function

```


## Exercise 7

```{r}
# Overall table_mm arithmetic mean, median, and geometric mean?






# Arithmetic mean, median, and geometric mean of table_mm within each clarity category






```

_Add your comment here_


## Exercise 8 (optional)

```{r}
# Create gmean2() that computes the geometric mean 
#   that uses the original definition






```


## Exercise 9 (optional)

```{r}
# Create a function that computes the harmonic mean







```

## Exercise 10 (optional)

_Do derivation on paper, unless you know how to write LaTeX code_
